Approximate Code: A Cost-Effective Erasure Coding Framework for Tiered Video Storage in Cloud Systems

### 2019-04-20 ApproximateCode.tex
version 3.8.2

\documentclass[sigconf]{acmart}

@@

To address this problem, in this paper, we propose Approximate Code, which is an erasure coding framework for video applications in cloud storage systems. The key idea of Approximate Code is distinguishing the important data and unimportant data in videos with different capabilities of fault tolerance. On one hand, for important data, Approximate Code provides triple parities to provide high reliability. On the other hand, single/double parities are applied for unimportant data, which can save the storage cost and accelerate the recovery process. To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop systems. The results show that, compared to traditional 3DFTs using various erasure codes such as RS, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 60\%, saves the storage cost by up to 10\%, increase the recovery speed by up to 1.5X when single disk fails, and can reconstruct the whole video data via fuzzification when triple disks fail.

\end{abstract}

@@

\subsection{Overview of Approximate Code Framework}
The Approximate Code mainly includes three operations: code segmentation, structure selection and code generation, as shown in Figure \ref{fig-framework}.

\subsubsection{Code Segmentation}
For any type of input erasure code, we assume that its fault tolerance is $x$. The Approximate Code first splits its parity block into two parts: local and global. The former verifies all important and non-critical data, while the latter only verifies important data. Code segmentation are designed to ensure that local parities can tolerate any $r$ node failures, so the fault tolerance of non-critical data is $r$. For important data, the code segmentation ensures that the parity block of important data can be completely recombined into the original $x$DFTs erasure code scheme.

\subsubsection{Structure Selection}
The Approximate Code framework then choose the Structure for the input erasure code.
Approximate Code distribute important and unimportant data separately and mainly in two structure. As shown in Figure \ref{fig-ap-414}, in \emph{Structure 1}, important data occupies 1 of $s$ blocks in each node, and in \emph{Structure 2}, it occupies 1 of all $h$ data arrays.
We define that $h=s$, so in \emph{Structure 1} and \emph{Structure 2},important data accounts for $1/h$ of all data.

Figure \ref{fig-framework} shows the process of turning a code(assume that it is XXX) to Approximate XXX code. XXX-code has two parities chunks, the horizontal and the diagonal. Approximate Code framework define the former as local parity chunk and the latter as the global parity chunk. Then \emph{Structure 2} is selected and the Approximate XXX Code is a 16-node system.

\subsubsection{Code Generation}

The construction of the Approximate Code is determined by 3 parameters $k$, $r$ and $h$. 
In a $n$-node array, $k$ of them are data nodes and $r=n-k$ nodes are for local parity, where each node can be divided into multiple blocks, and we label the number of blocks in a node as $s$.
Approximate Code are designed for $h$ arrays, therefore it includes $k*n$ data nodes and $r*h$ local parity nodes.
Besides them, $3-r$ nodes are designed for global parity, and the total number of nodes in Approximate Code ($k,r,h$) is $$h*(k+r) +3-r$$

In each array, $r$ nodes are local parity nodes, which is encoded by the rest $k$ data nodes in the array.
In addition, there are another $3-r$ global nodes, which are calculated only by the important data blocks. It should be point out that the global parity nodes should be placed in different nodes and should be different from the data nodes.

The number of important data blocks is $h \times k$, and they generate $h \times (3-r)$ global parity blocks.
To sum up, the number of blocks involved in the Approximate Code is 
$$(k+r)h^2 + (3-r) h$$

Approximate Code guarantees that for each array, the unimportant data can tolerate any $r$ node failures. Usually, $r$ is equal to 1 or 2, which covers most node failure scenarios, while important data are provided 3DFTs.

The construction of Approximate Code (4,1,4, \emph{Structure 1}) and Approximate (3,1,3, \emph{Structure 2}) can be illustrated by Figure \ref{fig-ap-414},

%As mentioned before, if it is considered that the nodes from the same column belong to the same node, this example includes 4 arrays with 7 nodes; otherwise, it includes 4 arrays with 22 nodes.
\iffalse
\begin{figure}[]
\centering
\includegraphics[width=\linewidth]{photo/AP-kmha-v7.pdf}
\caption{A sample of Approximate Codes $(4,1,4)$ in \emph{Structure 1}, and Approximate Code $(3,1,3)$ in \emph{Structure 2}.
Data nodes are marked as $N_i$, important data are marked as water green, local parity nodes are marked as orange and global parity nodes are marked as red.
}
\label{fig-ap-414}
\end{figure}

@@

\subsection{RS-based Approximate Code}
The construction of the Approximate Code based on RS is simple. In \emph{Structure 1}, the encoding unit is block. A horizontal RS parity is performed on the corresponding block in each node to generate a local parity block. At the same time, the important data blocks is horizontally verified by RS and generate multiple global check blocks.

In \emph{Structure 2}, the encoding unit is node.
We perform horizontal RS parity in each array to generate local parity nodes. The global parity node is generated only by the important data array.

Figure \ref{fig-ap-rs} is the RS generation matrix with $k=4$ and $r=1$.
It shows that to ensure that the coefficients of the local and the global parity are linearly independent is easy. If necessary, Approximation Code can easily achieve higher reliability guarantees based on RS, but in most cases this is excessive, so we will not discuss it here.

\subsection{XOR-based Approximate Code}
Since we mainly provide 3DFTs for important data, we prefer to construct Approximate Code with several RAID6-based codes to provide faster encoding and reconstruction speed than RS. This section introduce tipical cases of the construction of XOR-based Approximate Code ($5,1,6$, \emph{Structure 1}) and ($4,2,4$, \emph{Structure 2}).

\subsubsection{RAID5-TIP Approximate Code}

@@

\subsubsection{EVENODD-STAR Approximate Code}
Figure \ref{fig-ap-STAR} shows the construction of Approximate Code ($5,2,4$) in \emph{Structure 2} based on EVENODD \cite{blaum1995evenodd} and STAR \cite{huang2008star}. 
EVENODD is a tipical RAID6 erasure code scheme, while STAR is a 3DFTs extension scheme of EVENODD. In this case, important data blocks are distributed in array 0, while unimportant data blocks occupy the rest arrays. 
$LP_{i,0}$ to $LP_{i,3}$ consist the horizontal parity nodes and $LP_{i,4}$ to $LP_{i,7}$ consist diagonal parity nodes for array $i$. So the form of every array fit the construction of EVENODD. Because the STAR code is constructed just by adding a reverse parity chain to the EVENODD code. 
The $GP$ is the anti-diagonal parity node and guarantee important data nodes form the construction method of STAR, which ensures the 3DFTs.

\begin{figure}[]
\centering
\includegraphics[width=0.45\textwidth]{photo/AP-523.pdf}
\caption{The XOR-based Approximate Code ($5,2,4$), constructed based on EVENODD and STAR code. $LP$ represent the local parity and $GP$ represent the global parity.}
\label{fig-ap-STAR}
\end{figure}

\includegraphics[width = 0.98 \linewidth]{photo/EVENODD-STAR.pdf}

\subsection{Case Study}
This section describe the decoding methods in different cases of node failure based on \emph{Structure 1} and \emph{Structure 2}.

@@

///////////////////////
Under the random probability model of nodes, the probability of failure of the Approximate Code under 4 node damage is
\begin{equation}
    P_{failure} = \frac{C_{k+3}^4}{C_{(k+r)h+3-r}^4}
\end{equation}
which is the 4 node failure situation in $k$ important data nodes and 3 important parity nodes. For example, the failure situation of Approximate Code ($4,1,4$, \emph{Structure 2}) probability is 0.478\%.

@@

\begin{table}[]
\centering 
\caption{Comparison of storage overhead and fault tolerance between Ap-Code (short for Approximate Code), RS and several XOR-based codes.}\label{tab-AS-RS-AP}
\begin{tabular}{|c|c|c|c|}
\hline
EC & \begin{tabular}[]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[]{@{}c@{}}Fault \\ Tolerance\end{tabular} & \begin{tabular}[]{@{}c@{}}Single Node\\Update Cost\end{tabular} \\ \hline
RS($k,r$) & $(k+r)/k$ & $r$ & r \\ \hline
EVENODD($k,2$) & $(k+2)/k$ & 2 & 2 \\ \hline
TIP-code/STAR($k,3$) & $(k+r)/k$ & 3 & 3 \\ \hline
\begin{tabular}[]{@{}c@{}}Ap-Code\\ ($k,r,h$)\end{tabular} & $\frac {(k+r)h+3-r}{k \times h}$ & r to 3 & $r+\frac{3-r}{h}$ \\ \hline
\end{tabular}
\end{table}

\section{Implementation}\label{Implementation}
\begin{figure}[htb]
\centering
\includegraphics[height = 6.5cm]{photo/implementation-V2.pdf}
\caption{Overview of Approximate Code implementation}
\label{fig-implementation}
\end{figure}

@@

\subsection{Data Segmentation and Distribution module}
The data segmentation module splits the video file stream into multiple data segments and automatically discriminates the important data. A natural approach is to follow the GOP segmentation. According to the \ref{video storage}, the GOP of the encoded video starts with an I frame, and all the data in that GOP depends on it for decoding, so we define it as important data and divide the GOP into I frames (important part) and other data. (unimportant part).

@@

\subsection{Approximate Code module}
The Approximate Code module is responsible for encoding and decoding important and unimportant data and completely recovering the data within fault tolerance. For data that cannot be recovered, the Approximate Code module transmits it to the video recovery module for approximate recover videos.

@@

\subsection{Data Fuzzification and Video Recovery}
In the approximate recovery mode, the remaining data and important data are transferred to this module. Using a series of methods described in Section \ref{video storage}, frames that suffer from frame loss will be recovered using the interpolation algorithm; the corrupted frames will be processed into fuzzy images and approximately recovered by superpixel techniques.

\section{Approximate Recovery}\label{ap-recovery}

\begin{figure*}\label{fig-node-lost}
\subfigure{
    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-4-disks.eps}
}
\subfigure{
    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-5-disks.eps}
}
\subfigure{
    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-6-disks.eps}
}
\subfigure{
    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-8-disks.eps}
}
\caption{Comparison of the data retention  between approximate storage and common methods when node is unrecoverable.}\label{fig-node-lost}
\end{figure*}

@@

\subsection{Frame Recovery ????}

@@

The environment of our experiment is listed below………….////////\par

\subsection{Numerical Results of Mathematical Analysis}
\subsubsection{Encoding Time Analysis}
From the Figure xx a), we could find out that the AP code encodes largely faster than RS ($k$, $3$). The rate of optimisation between AP($k$, $1$, $6$) and RS ($k$, $3$) is from 976.4\% (3 nodes’ case) to 849.2\% (13 nodes’ case), as the encoding time of AP codes multiplies about 4.7 times and that of RS code multiplies about 4.2 times. The Figure xx b) and c) illustrate that the effet of Star code and Tip code is similar, and the difference between them and AP code is not very large. The rate of optimisation between AP ($k$, $1$, $6$) and Star ($k$, $3$) is from 125.6\% (3 nodes’ case) to 127.3\% (17 nodes’ case). According to Figure xx d), we could see that AP code largely reduces the encoding time, comparing to LRC method. The rate of optimisation between AP code (k, 1, 4) and LRC (4k, 2, 4) is from 596.0\% (3 nodes’ case) to 615.8\% (13 nodes’ case); and the rate of optimisation between AP code ($k$, $1$, $6$) and LRC ($6k$, $2$, $6$) is from 684.0\% to 443.1\%. Considering the optimisation rate, AP code ($k$, $1$, $4$) is the best among the four.\par

>>>>

% !TEX TS-program = pdflatex
\documentclass[sigconf]{acmart}

@@

To address this problem, in this paper, we propose Approximate Code, which is an erasure coding framework for video applications in cloud storage systems. The key idea of Approximate Code is distinguishing the important data and unimportant data in videos with different capabilities of fault tolerance. On one hand, for important data, Approximate Code provides triple parities to provide high reliability. On the other hand, single/double parities are applied for unimportant data, which can save the storage cost and accelerate the recovery process. To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop systems. The results show that, compared to traditional 3DFTs using various erasure codes such as RS, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 60\%, saves the storage cost by up to 10\%, increase the recovery speed by up to 1.5X when single disk fails, and can reconstruct the whole video data via fuzzification when triple disks fail.
                                                                    q
\end{abstract}

@@

\subsection{Overview of Approximate Code Framework}
The Approximate Code mainly includes three operations: code segmentation, structure selection and code generation. We use Figure \ref{fig-framework} to illustrate our design.

\subsubsection{Code Segmentation}
For an input erasure code, we assume that its fault tolerance is $x$. The Approximate Code first splits its parity block into two parts: local and global. The former verifies all important and non-critical data, while the latter only verifies important data. Code segmentation are designed to ensure that local parities can tolerate any $r$ node failures, so the fault tolerance of non-critical data is $r$. For important data, the code segmentation ensures that the parity block of important data can be completely recombined into the original $x$DFTs erasure code scheme.

In the example, a 3DFTs erasure code with 4 data chunks and 3 parity chunks is input, and its 3 parity chunks are separated into two local and one global parity chunks.

\subsubsection{Structure Selection}
The Approximate Code framework then choose the structure for the input erasure code.
There are two main structures that distribute important and unimportant data in different ways.
As shown in Figure \ref{fig-framework}, in \emph{Structure 1}, important data occupies 1 block in each node, and in \emph{Structure 2}, it occupies 1 data arrays.
We specify that in \emph{Structure 1}, the ratio of important data to each node is $1/h$, thereby ensuring that the number of important data in both \emph{Structure 1} and \emph{Structure 2} just fills up $k$ nodes.

Since \emph{Structure 1} distributes important data across each node, it guarantees a more balanced load. \emph{Structure 2} concentrates important data into an array, and provides greater reliability for important data. A detailed analysis of this will be presented in \ref{evaluation}.

\subsubsection{Code Generation}
After code segmentation and structure selection, the Approximate Code Framework generates an approximate form of the input erasure code.

The construction of the Approximate Code is determined by 4 parameters $k$, $r$, $g$ and $h$. 
In a $n$-node array, $k$ of them are data nodes and $r=n-k$ nodes are for local parity, where each node can be divided into multiple blocks.
Approximate Code are designed for $h$ arrays, therefore it includes $k*h$ data nodes and $r*h$ local parity nodes.
Besides them, $g$ nodes are designed for global parity, which are calculated only by the important data blocks. The total number of nodes in Approximate Code ($k,r,g,h$) is 
$h*(k+r) + g$.

Approximate Code guarantees that the unimportant data can tolerate any $r$ node failures and the important data can tolerate any $r+g$ node failures.
Since the 3DFTs is a tipical configuration, we mainly discuss the situation of $r+g=3$, so $r$ is usually set to 1 or 2.

\iffalse
\begin{figure}[]
\centering
\includegraphics[width=\linewidth]{photo/AP-kmha-v7.pdf}
\caption{A sample of Approximate Codes $(4,1,4)$ in \emph{Structure 1}, and Approximate Code $(3,1,3)$ in \emph{Structure 2}.
Data nodes are marked as $N_i$, important data are marked as water green, local parity nodes are marked as orange and global parity nodes are marked as red.
}
\label{fig-ap-414}
\end{figure}

@@

\subsection{Approximate RS Code}
For RS(k,p), it can be seen that it provides $p$ independent horizontal parity nodes for $k$ data nodes. Therefore, the code segmentation for RS is arbitrary, that is, it supports any $r=p-g(0<g<p)$. RS also supports both two structures.

For the situation shown in Figure \ref{fig-framework}, we consider the input erasure code as RS(4,3). It is divided into two local parities and one global parities with the \emph{Structure 2} and it generate Approximate RS Code (4,2,1,3,\emph{Structure 2}).
As a result, the unimportant data constitutes RS(4,2), and the important data constitutes RS(4,3).

\subsection{XOR-based Approximate Code}
Since we mainly provide 3DFTs for important data, we prefer to construct Approximate Code with several XOR-based codes to provide faster encoding and reconstruction speed than RS. This section introduce two tipical construction of XOR-based Approximate Code, Approximate STAR Code and Approximate TIP Code.

\subsubsection{Approximate STAR Code}
Figure \ref{fig-ap-STAR} shows the construction of Approximate STAR Code ($5,2,1,3$) in \emph{Structure 2}

based on EVENODD \cite{blaum1995evenodd} and STAR \cite{huang2008star}. 
EVENODD is a tipical RAID6 erasure code scheme, while STAR is a 3DFTs extension scheme of EVENODD. In this case, important data blocks are distributed in array 0, while unimportant data blocks occupy the rest arrays. 
$LP_{i,0}$ to $LP_{i,3}$ consist the horizontal parity nodes and $LP_{i,4}$ to $LP_{i,7}$ consist diagonal parity nodes for array $i$. So the form of every array fit the construction of EVENODD. Because the STAR code is constructed just by adding a reverse parity chain to the EVENODD code. 
The $GP$ is the anti-diagonal parity node and guarantee important data nodes form the construction method of STAR, which ensures the 3DFTs.

\begin{figure}[]
\centering
\includegraphics[width=0.6\linewidth]{photo/AP-523.pdf}
\caption{The XOR-based Approximate Code ($5,2,4$), constructed based on EVENODD and STAR code. $LP$ represent the local parity and $GP$ represent the global parity.}
\label{fig-ap-STAR}
\end{figure}

\includegraphics[width =\linewidth]{photo/EVENODD-STAR.pdf}

\subsubsection{Approximate TIP Code}

@@

\iffalse
\subsection{Case Study}
This section describe the decoding methods in different cases of node failure based on \emph{Structure 1} and \emph{Structure 2}.

@@

///////////////////////
Under the random probability model of nodes, the probability of failure of the Approximate Code under 4 node damage is
\begin{equation}
    P_{failure} = \frac{C_{k+3}^4}{C_{(k+r)h+3-r}^4}
\end{equation}
which is the 4 node failure situation in $k$ important data nodes and 3 important parity nodes. For example, the failure situation of Approximate Code ($4,1,4$, \emph{Structure 2}) probability is 0.478\%.
\fi

@@

\begin{table}[]
\centering 
\caption{Comparison of storage overhead and fault tolerance between Ap-Code (short for Approximate Code), RS and several XOR-based codes.}\label{tab-AS-RS-AP}
\begin{tabular}{|c|c|c|c|}
\hline
EC & \begin{tabular}[]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[]{@{}c@{}}Fault \\ Tolerance\end{tabular} & \begin{tabular}[]{@{}c@{}}Single Node\\Update Cost\end{tabular} \\ \hline
RS($k,q$) & $(k+q)/k$ & $q$ & q \\ \hline
EVENODD($k,2$) & $(k+2)/k$ & 2 & 2 \\ \hline
TIP-code/STAR($k,3$) & $(k+r)/k$ & 3 & 3 \\ \hline
\begin{tabular}[]{@{}c@{}}Ap-Code\\ ($k,r,h$)\end{tabular} & $\frac {(k+r)h+3-r}{k \times h}$ & r to 3 & $r+\frac{3-r}{h}$ \\ \hline
\end{tabular}
\end{table}

\subsection{Implementation}\label{Implementation}
\begin{figure}[htb]
\centering
\includegraphics[height = 5cm]{photo/implementation-V2.pdf}
\caption{Overview of Approximate Code implementation}
\label{fig-implementation}
\end{figure}

@@

\subsubsection{Data Segmentation and Distribution module}
The data segmentation module splits the video file stream into multiple data segments and automatically discriminates the important data. A natural approach is to follow the GOP segmentation. According to the \ref{video storage}, the GOP of the encoded video starts with an I frame, and all the data in that GOP depends on it for decoding, so we define it as important data and divide the GOP into I frames (important part) and other data. (unimportant part).

@@

\subsubsection{Approximate Code module}
The Approximate Code module is responsible for encoding and decoding important and unimportant data and completely recovering the data within fault tolerance. For data that cannot be recovered, the Approximate Code module transmits it to the video recovery module for approximate recover videos.

@@

\subsubsection{Data Fuzzification and Video Recovery}
In the approximate recovery mode, the remaining data and important data are transferred to this module. Using a series of methods described in Section \ref{video storage}, frames that suffer from frame loss will be recovered using the interpolation algorithm; the corrupted frames will be processed into fuzzy images and approximately recovered by superpixel techniques.

\iffalse
\section{Approximate Recovery}\label{ap-recovery}
\begin{figure*}\label{fig-node-lost}
\subfigure{
    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-4-disks.eps}
}
\subfigure{
    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-5-disks.eps}
}
\subfigure{
    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-6-disks.eps}
}
\subfigure{
    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-8-disks.eps}
}
\caption{Comparison of the data retention  between approximate storage and common methods when node is unrecoverable.}\label{fig-node-lost}
\end{figure*}

@@

\subsection{Frame Recovery ????}
\fi

@@

The environment of our experiment is listed below.

\subsection{Numerical Results of Mathematical Analysis}
\subsubsection{Encoding Time Analysis}
From the Figure xx a), we could find out that the AP code encodes largely faster than RS ($k$, $3$). The rate of optimisation between AP($k$, $1$, $6$) and RS ($k$, $3$) is from 976.4\% (3 nodes case) to 849.2\% (13 nodes case), as the encoding time of AP codes multiplies about 4.7 times and that of RS code multiplies about 4.2 times. The Figure xx b) and c) illustrate that the effet of Star code and Tip code is similar, and the difference between them and AP code is not very large. The rate of optimisation between AP ($k$, $1$, $6$) and Star ($k$, $3$) is from 125.6\% (3 nodes case) to 127.3\% (17 nodes case). According to Figure xx d), we could see that AP code largely reduces the encoding time, comparing to LRC method. The rate of optimisation between AP code (k, 1, 4) and LRC (4k, 2, 4) is from 596.0\% (3 nodes case) to 615.8\% (13 nodes case); and the rate of optimisation between AP code ($k$, $1$, $6$) and LRC ($6k$, $2$, $6$) is from 684.0\% to 443.1\%. Considering the optimisation rate, AP code ($k$, $1$, $4$) is the best among the four.\par
